\chapter{Eightieth Birthday Speech}
\label{birthday}

\begin{verse}
Eighty years my life has seen \\
And what a wonderful life it's been \\
With a happy childhood right from birth \\
My parents were known as the 'salt of the earth' \\
\end{verse}

\begin{verse}
My `growing up years' were spent with 3 brothers \\
We each took a turn at tormenting the others! \\
We had gas masks and rationing and bombs from the Hun \\
But we still managed to have lots of fun. \\
\end{verse}

\begin{verse}
Come the time to leave school and go to college \\
(something had to be done to broaden my knowledge) \\
From there I emerged with a lovely career \\
Which I pursued and enjoyed up to the sixth year \\
\end{verse}

\begin{verse}
In 1952 one day into my life came Mr Bray \\
I knew that he was here to stay \\
('E fairly took my breath away) \\
\end{verse}

\begin{verse}
For some strange reason he liked me too \\
And for 56 years our romance has stayed true \\
He is kind and generous, funny and wise \\
How could I have deserved such a prize? \\
\end{verse}

\begin{verse}
In 1953 we were wed \\
And then Tony up and took me to -- Turkey \\
Where he had to work but I had the time \\
To accustom myself to a different clime. \\
\end{verse}

\begin{verse}
We traveled around the great country a lot \\
For culture and history it's really a spot \\
But we always felt the magical pull \\
Of getting back to Istanbul! \\
\end{verse}

\begin{verse}
After three years we went back to UK \\
And of course life resumed in a different way \\
We were sad that our Turkish days were over \\
But all of a sudden we landed in clover! \\
\end{verse}

\begin{verse}
Because, after a 7-year wait came Elizabeth Ann \\
I couldn't believe what we'd got in the pram! \\
How loving and caring and clever she is \\
We are so lucky to have 'our Liz'. \\
\end{verse}

\begin{verse}
I do so wish she was here today \\
It breaks my heart that she is so far away. \\
\end{verse}

\begin{verse}
When she was two we moved once more \\
This time to the West African shore, \\
Nigeria gave us some panic and fears \\
But we managed to stay for 11 years! \\
\end{verse}

\begin{verse}
During which time arrived Richard our boy \\
He completed the family, that was a joy \\
We are proud of what he's achieved and done \\
He really is a remarkable son! \\
\end{verse}

\begin{verse}
I'm so glad he's here today \\
But it breaks my heart that they live far away. \\
\end{verse}

\begin{verse}
And then we came down to live in SA \\
At that stage we had no intention to stay \\
But we've been here now for 36 years \\
And we share in South Africa's hopes and fears. \\
\end{verse}

\begin{verse}
Our kids and their mates in the fullness of time \\
Gave us eight lovely grandchildren all healthy and fine \\
I think that by now, you have to agree \\
That Lady Luck has smiled on me. \\
\end{verse}

\begin{verse}
Friends are the fabric of everyday life \\
They support you in happiness, sickness and strife \\
And I look at you all here with us today \\
Bless you and thank you for sharing my day. \\
\end{verse}

\begin{verse}
Someone else has looked after me \\
And helped me to be the person you see \\
And standing here I am bound to recall \\
The love of God which surrounds us all. \\
\end{verse}
