\chapter{Foreword}

A couple of years ago, when I asked mum to consider writing her
memoirs, she protested vociferously that her life wasn't interesting
and no-one would want to read about it. I told her that in fact she
owed it to her grandchildren as a legacy and that I was sure they
would be interested. And so, after some more persuasion, she rose to
the challenge with her characteristic gritty resolve and started
writing.

I have only recently realised that mum is one of the most courageous
and resilient women I have ever known. Like many of her generation,
she has often had to cope with very challenging
circumstances. However, she not only continues to deal with what life
throws at her, but invariably finds a reason to be grateful and happy
with her lot. Many of us could take a leaf out of book!

Mum has a very active mind. She took great delight in sharing dad's
love of astronomy, enjoys a robust discussion about current affairs
and, in particular, follows the international tennis circuit with
great enthusiasm. She is also very creative and her outlets have
included playing the piano, sewing and cake decorating. Clearly she
also writes a good story!  However, her writing has also extended to
creating poems for various occasions, one most notably being her 80th
birthday celebration.

In writing her memoirs, mum has provided an insight to a varied and
interesting life and has revealed the character and determination that
I so admire. Often families know very little of the life behind the
older generation and I am so pleased that mum took the time and effort
to put pen to paper so that questions about her life can be asked and
answered while it is still possible. I am very privileged to have her
as a mum (although I admit I haven't always thought so!).

I have been amazed at the level of interest mum's memoirs have
generated. Mum's initial writing prompted questions which required her
to write some more until she finally cried ``stop!''. I could not have
foreseen how the project would gather momentum and become a true
collaborative effort among her grandchildren. So thank you mum for
rising to the challenge and to all the kids for the part they have
played in bringing this all together -- the typing and editing,
finding and scanning photographs, and research even, which uncovered a
newspaper article about the bombing in Lagos! A mammoth task, but the
result is a beautiful book, a tribute to mum's life captured on paper.

Liz Preston

July 2013
